Figures and Tables

### 2020-10-13 paper/figures_tables.Rmd
deleted old figures.

theme_set(theme_bw())
```

```{r functions}

# Extract parameters from fitted distributions to the data
build.fits.df <- function(x){

  nm <- deparse(substitute(x))

  x %>%
  map(., `[`, c("estimate", "sd", "loglik", "n")) %>%
  map(as_tibble) %>%
  bind_rows()
}

@@

The way we are fitting the data can be visualized as follows, where each curve represents the population, an individual, or a family group:

```{r data}
# Get the data loaded. We are removing the one value with zero since it won't allow fitting.

load("data/newpointlocs.rda")

df <- newpointlocs %>%
  dplyr::filter(mpm != 0) %>%
  ungroup() %>%
  mutate(Bird_ID = paste0("B", Bird_ID),
         sqR2n = sqrt(R2n)) %>%
  group_by_("id", "burst") %>%
  mutate(cumdt = cumsum(dt)/60) %>%
  ungroup()
```

```{r fig.width=10}
pop_dens_plot <- df %>%
  ggplot(., aes(x = mpm)) +
  geom_line(stat = "density", color = "grey", lwd = 1) +
  #geom_line(aes(x = dist, group = id), stat = "density", alpha = 0.4) +
  geom_vline(xintercept = 0, color = "grey") +
  geom_hline(yintercept = 0, color = "grey") +
  ylim(0, 0.05) +
  labs(title = "Population") +
  theme_classic()

ind_dens_plot <- df %>%
  ggplot(., aes(x = mpm)) +
  geom_line(stat = "density", color = "red", lwd = 1) +
  geom_line(aes(x = mpm, group = id), stat = "density", alpha = 0.4) +
  geom_vline(xintercept = 0, color = "grey") +
  geom_hline(yintercept = 0, color = "grey") +
  ylim(0, 0.055) +
  labs(title = "Individual") +
  theme_classic()

fam_dens_plot <- df %>%
  filter(., fam_g != "unknown") %>%
  ggplot(., aes(x = mpm)) +
  geom_line(stat = "density", color = "red", lwd = 1) +
  geom_line(aes(x = mpm, group = fam_g), stat = "density", alpha = 0.4) +
  geom_vline(xintercept = 0, color = "grey") +
  geom_hline(yintercept = 0, color = "grey") +
  ylim(0, 0.055) +
  labs(title = "Family") +
  theme_classic()

fam_zoom <- fam_dens_plot +
  coord_cartesian(ylim = c(0, 0.01), xlim = c(50, 210))

```{r}

ind_zoom <- ind_dens_plot +
  coord_cartesian(
    ylim = c(0, 0.01),
    xlim = c(60, 180))

ind_grob <- ggplotGrob(ind_zoom)

ind_dens_plot +
  annotation_custom(grob = ind_grob, xmin = 50 , xmax = 200 , ymin = 0.02 , ymax = 0.05)
```

```{r}

fam_zoom <- fam_dens_plot +
  coord_cartesian(
    ylim = c(0, 0.01),
    xlim = c(50, 210))

fam_dens_plot +
  annotation_custom(grob = ggplotGrob(fam_zoom), xmin = 50 , xmax = 200 , ymin = 0.02 , ymax = 0.05)
```

```{r}
ggarrange(ind_dens_plot, fam_dens_plot, nrow = 2)
```

>>>>

@@

# Layout of steps of one simulation run

# Figure with variation for parameter estimates

# Table: Info criteria for family and individual levels

# Facetted plot for seed dispersal distances

# Density figures from which step and grt are sampled from
